In-silico molecular enrichment and clearance of the human intracranial space

### 2025-01-30 paper/main.tex
Tweaks in the acknowledgments

All authors express their gratitude to Prof.~Jürgen Reichenbach for
generously sharing the multi-modal human MR data, and to Prof. Erlend
Hodneland for facilitating this data exchange. M.E.R. acknowledges the
support of the Foundation Kristian Gerhard Jebsen via the K.~G.~Jebsen
Center for Brain Fluid Research and the Research Council of Norway via
grant \#324239 (EMIx). Simulations were performed on the Experimental
Infrastructure for Exploration of Exascale Computing (eX3), which is
financially supported by the Research Council of Norway under contract
270053. 
M.C. acknowledges support from the RCN grant \#324239 (EMIx).
M.K. acknowledges support from the RCN grant \#303362.
The figures 1A, 1D, 2C, 3C, 5A and 6A were created in Biorender.

>>>>

All authors express their gratitude to Prof.~Jürgen Reichenbach for
generously sharing the multi-modal human MR data, and to Prof. Erlend
Hodneland for facilitating this data exchange. M.E.R.~acknowledges
support from Stiftelsen Kristian Gerhard Jebsen via the K.~G.~Jebsen
Centre for Brain Fluid Research. M.E.R.~and M.C.~acknowledge support
from the Research Council of Norway (RCN) via grant \#324239
(EMIx). Simulations were performed on the Experimental Infrastructure
for Exploration of Exascale Computing (eX3), which is financially
supported by the RCN under contract 270053. M.K.~acknowledges support
from the RCN grant \#303362. The figures 1A, 1D, 2C, 3C, 5A and 6A
were created in Biorender.
